The watershed transform in ITK - discussion and new developments

### 2006-05-15 article/Article.tex
Minor additions to article
I've kept the first hill climbing algorithm because I recently had a reviewer
of an article claim that version was the "one true" hill climbing algorithm.
It is good to be complete, anyway.

darcs-hash:20060515054736-fafb9-e667ea21d523943faeca93b1bf9ccfd3fe50f87f.gz

\subsection{Efficiency issues}
The procedure outlined above introduces a lot of additional steps,
some of which could be reasonably computationally expensive
(i.e. recursive erosion). Other steps have also been mentioned in
passing ({\em lower completion} in Section \ref{sect:history} that may
be potentially time consuming. Fortunately we will discover in Section
\ref{sect:algorithms} that the appropriate choice of algorithm implementing the
watershed transform will carry out these steps implicitly.

@@

{\em Is it really needed to present this algorithm given that there is
no lower completion ? Isn't it enough to notice somewhere that an
algorithm exist without lower completion, and which require to put
all the pixels in the queue ?}

@@

There are at least two reasons why we shouldn't use this
approach. Firstly, the lower completion step is explicit, which we'd
like to avoid and secondly {\em all} non minima pixels are placed on the
queue, which means that the queue length is almost the same as the
number of image pixels, increasing the overhead of queue
management. We shall see that it is only necessary to have the pixels
on the borders of the regions in the queue.

@@

It must be noticed that this algorithm never propagate watershed
lines, and so produce very thin watershed lines.

@@

ITK watershed clearly produce a wrong segmentation in that case.
The result of the morphological watershed is quite good, even if not perfect:
there is some curves in the separation line of the two labels. This is the
result of the distance approximation in the watershed algorithm.

>>>>

\subsection{Efficiency issues}
The procedure outlined above introduces a lot of additional steps,
some of which could be reasonably computationally expensive
(i.e. recursive erosion). Other steps have also been mentioned in
passing ({\em lower completion} in Section \ref{sect:history}) that may
be potentially time consuming. Fortunately we will discover in Section
\ref{sect:algorithms} that the appropriate choice of algorithm implementing the
watershed transform will carry out these steps implicitly.

@@

@@

This is the most basic version of hill climbing, and is presented here
for completeness. There are at least two reasons why we shouldn't use
this approach. Firstly, the lower completion step is explicit, which
we'd like to avoid and secondly {\em all} non minima pixels are placed
on the queue, which means that the queue length is almost the same as
the number of image pixels, increasing the overhead of queue
management. We shall see that it is only necessary to have the pixels
on the borders of the regions in the queue.

@@

It should be noted that this algorithm never propagates watershed
lines, and that the watershed lines it produces have a width of 1 pixel.

@@

ITK watershed clearly produce a wrong segmentation in that case.
The result of the morphological watershed is quite good, even if not perfect:
there are some curves in the separation line of the two labels. This is the
result of the distance approximation in the watershed algorithm.
